\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 poster/main.tex
update poster

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)) $\todo{K-divergence}$.
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach samples noise from $\mathsf{Lap}(\Delta \alpha, \frac{1}{\epsilon})$ with mean $\Delta \alpha$ and scale $\frac{1}{\epsilon}$. But noise here is proportional to $\ell_1$ norm, which grows linear with the dimension.. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism (v.s. global sensitivity) to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.

  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} gives the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior distribution configuration.
  In the baseline approach (LapMech {\small with noises being postprocessed to the closest integer}), it is enough to add noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions since it's equivalent to histogram
  (posteriors of adjacent data sets differ only in two dimensions),
  giving us the red points in plots. Without knowing equivalence, LapMech adds noise scaled to sensitivity proportional to dimensionality, giving us green points.
  Points in blue are given by the $\hexpmech$.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.304\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

>>>>

\begin{block}{Objectives}
% \begin{columns} % Subdivide the first main column
% \begin{column}{.69\textwidth}
\begin{enumerate}
\item Designing a differentially private Bayesian inference mechanism.
\item Measuring accuracy with a metric over distributions (Hellinger distance ($\hellinger$)), $f$-divergence, etc.
% \item Calibrating the noise w.r.t sensitivity of the (Hellinger distance).
% \item Applying smooth sensitivity in mechanism to achieve better accuracy.
%         (Fig. \ref{fig_sensitivity} shows that local sensitivity of Hellinger distance is very steep and much higher in the edges but very smooth in central part).
\end{enumerate}
% \end{column}
% \begin{column}{.28\textwidth}
% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.85\textwidth]{poster_0.eps}
% say something about beta...
% \caption{\footnotesize{Local sensitivity of Hellinger}}
% \label{fig_sensitivity}
% \end{figure}
% \vspace{.1cm}
% \end{column}
% \end{columns}

@@

\begin{block}{Differentially Private Bayesian Inference and Motivations}
Releasing a differentially private posterior $\betad (\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$.
\begin{columns} % Subdivide the first main column
\begin{column}{.69\textwidth}
\begin{enumerate}
  \item  Baseline approach is Laplace mechanism (LapMech) with sensitivity proportional to $\ell_1$ norm. But we measure results by a different metric and sensitivity grows linear with the dimension. Motivated by this, we calibrate the noise w.r.t sensitivity of the accuracy metric ($\hellinger$). %(v.s. the $\ell_1$ norm in baseline approach).} \todo{} % \todo{give formula of hellinger Distance, give the Dirichlet distribution, no need to formal expression, Laplace with mean and scale in 2 dimension.}
  \item Maximum sensitivity of $\hellinger$ over $\betad$ distributions achieve value at edge as in Fig. \ref{fig_sensitivity}. But it's very low when move away from edge. Motivated by this, we apply smooth sensitivity in mechanism to improve accuracy.
  %{sensitivity is maximize when plot of hellinger distance of alpha and beta variance between adjacent data bases, of varying }
\end{enumerate}
\end{column}
\begin{column}{.28\textwidth}
\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{poster_0.eps}
\caption{\footnotesize{Sensitivities of $\hellinger$ over $\betad$}}
\label{fig_sensitivity}
\end{figure}
% \vspace{.1cm}
\end{column}
\end{columns}

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] Red: LapMech adding noise with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data differ only in two dimensions).
  \item[-] Blue: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.311\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.311\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}
